Example Manuscript Template for a Data Analysis Project

### 2024-06-22 products/manuscript/Manuscript.qmd
add updates to Manuscript

- The dataset Electric_Vehicle_Population_Data.csv was imported.
- Summary statistics and data types were displayed to understand the initial structure and content of the data.

@@

>>>>

- The dataset Electric_Vehicle_Population_Data.csv was imported.
- Summary statistics and data types were displayed to understand the initial structure and content of the data.
- UPDATE (6.17.2024) - Downloaded IRS tax data to join with the EV data by zip code
  - Tax data provides many financial variables that we will include in our models (i.e. can we predict the amount of EVs per zip code based off tax data?)
- Added a geojson file to draw zip codes on a map, will use for visualizations but still figuring out how to elegantly filter the json

@@

**Statistical Model**
- First iteration of models
- Produced a few statistically significant tax metrics for predicting the number of EVs in a given county
- Washington demographics datasets could further enhance our analysis
